Linear analysis of the vertical shear instability in astrophysical disks

### 2015-02-02 appendix.tex
revised analysis part

\section{Local model for a global problem}
Here, we discuss the relation between the linear problem in the
VGSB framework and the global linear problem. We begin with the
axisymmetric linearized fluid equations in cylindrical co-ordinates, including
thermal relaxation, 
\begin{align}
\ii\sigma\delta P &=\frac{\p P}{\p z}\delta v_z + \gamma P
\left[\frac{1}{r}\frac{\p}{\p r}\left(r\delta v_r\right) + \frac{\p
    \delta v_z}{\p z}\right] + \frac{1}{t_c}\left(\delta P -
  \frac{P}{\rho}\delta\rho\right) + \hat{g}_c \frac{\p P}{\p r}\delta v_r,\\
  \ii\sigma\delta\rho &= \frac{\rho}{r}\frac{\p}{\p r}\left(r\delta v_r\right) + \frac{\p}{\p
  z}\left(\rho\delta v_z\right)  + \hat{g}_c\frac{\p\rho}{\p r}\delta v_r,\\
\ii\sigma\delta v_r &= \frac{1}{\rho}\frac{\p\delta P}{\p r} - 2\Omega
\delta v_\phi - \hat{g}_c\frac{\delta\rho}{\rho^2}\frac{\p P}{\p r},\\ 
\ii\sigma\delta v_\phi  &= \frac{\kappa^2}{2\Omega}\delta v_r +
r\frac{\p\Omega}{\p z}\delta v_z,\\
\ii \sigma\delta v_z &= \frac{1}{\rho}\frac{\p\delta P}{\p z} -
\frac{\delta \rho}{\rho^2}\frac{\p P}{\p z},
\end{align}
where the coefficients $\hat{g}_c=1$ are inserted to label terms
associated with the background radial disk structure.

>>>>

\section{Local model for a global problem}\label{global_corr}
Here, we discuss the relation between the linear problem in the
VGSB framework and the global linear problem. We begin with the
axisymmetric linearized fluid equations in cylindrical co-ordinates, including
thermal relaxation, 
\begin{align}
\ii\sigma\delta P &=\frac{\p P}{\p z}\delta v_z + \gamma P
\left[\frac{1}{r}\frac{\p}{\p r}\left(r\delta v_r\right) + \frac{\p
    \delta v_z}{\p z}\right] + \frac{1}{t_c}\left(\delta P -
  \frac{P}{\rho}\delta\rho\right) + \hat{g}_c \frac{\p P}{\p r}\delta v_r,\\
  \ii\sigma\delta\rho &= \frac{\rho}{r}\frac{\p}{\p r}\left(r\delta v_r\right) + \frac{\p}{\p
  z}\left(\rho\delta v_z\right)  + \hat{g}_c\frac{\p\rho}{\p r}\delta v_r,\\
\ii\sigma\delta v_r &= \frac{1}{\rho}\frac{\p\delta P}{\p r} - 2\Omega
\delta v_\phi - \hat{g}_c\frac{\delta\rho}{\rho^2}\frac{\p P}{\p r},\\ 
\ii\sigma\delta v_\phi  &= \frac{\kappa^2}{2\Omega}\delta v_r +
r\frac{\p\Omega}{\p z}\delta v_z,\\
\ii \sigma\delta v_z &= \frac{1}{\rho}\frac{\p\delta P}{\p z} -
\frac{\delta \rho}{\rho^2}\frac{\p P}{\p z},
\end{align}
where the coefficients $\hat{g}_c=1$ are inserted to label terms
associated with the background radial disk structure.
